Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-04-09 paper/paper.qmd
Edits to Effect Size and Power Analysis

Since the interaction effect was not statistically significant ($p > 0.05$), we proceeded to assess the effect size with the purpose to evaluate the practical significance of our findings. Our model yields  $R^2 = 0.0398$. While $R^2$ commonly used in regression analysis to a measure explained variance, determining the goodness of fit of a model. However, in ANOVA Model the $R^2$ value doesn't have a direct interpretation as the proportion of variance explained by regression model and it also does not directly reflect differences between group means. We use the $R^2$ value to report the effect that corresponds to Cohen’s f guidelines i.e. $| f |$ is approximately 0.20 as our  $R^2$ falls between the small-medium categories.Even though the statistical test did not yield significant results, this quantity suggests we have a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.

@@

This suggests that while our ANOVA results were not statistically significant, this may be due to insufficient power rather than the absence of any real effect. The observed effect sizes fall into the small range according to Cohen’s conventions, which typically require a larger sample size to detect reliably.

>>>>

Since the interaction effect was not statistically significant ($p > 0.05$), we proceeded to assess the effect size with the purpose to evaluate the practical significance of our findings. Our model yields  $R^2 = 0.0398$. While $R^2$ is commonly used in regression analysis to measure the proportion of variance and goodness of fit of the model, it can also be applied into ANOVA models. In that case, the $R^2$ value shows how much of the variation in the results can be explained by the different groups. However, it doesn't tell us how big or important the differences between the groups actually are.

We use this $R^2$ value to report the effect that corresponds to Cohen’s f guidelines, i.e. $| f |$ is about 0.20 since our $R^2$ falls between the small-medium categories. Even though the statistical test did not yield significant results, this quantity suggests we have approximately a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.

@@

This suggests that while our ANOVA results were not statistically significant -- possibly due to insufficient power rather than the absence of any real effect. The observed effect sizes fall into the small range according to Cohen’s conventions, which typically require a larger sample size to detect reliably.
